---
title: "team"
author: "Jacob Shoemaker, jshoemaker2249; Qinwen Yang; AngelQinwen"
date: "February 7, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Team Question Set

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
```


1. What is the overall number of chocolate bars rated?
```{r}
nrow(choco)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}
CountDate <- choco$Review.Date
table(CountDate)
barplot(table(CountDate))
```
3. How do ratings compare across different company locations? Focus on the three locations with the most ratings. (Hint: They are U.S.A., France, and Canada, but find them out using codes.)
```{r}
summary(choco$Company.Location)
```
4.
Create own question and answer:

#How many different companies located in France?


```{r}
OnlyFrance <- choco[(choco$Company.Location=="France"), ]
summary(OnlyFrance$Company)
UniqueCompany <- unique(OnlyFrance$Company)
summary(UniqueCompany)
length(UniqueCompany)
```
