---
title: "team"
author: "Jacob Shoemaker, jshoemaker2249; Qinwen Yang, AngelQinwen"
date: "February 7, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Team Question Set

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
```


1. What is the overall number of chocolate bars rated?
```{r}
nrow(choco)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.  

```{r}
CountDate <- choco$Review.Date
table(CountDate)
barplot(table(CountDate))
``` 


3. How do ratings compare across different company locations? Focus on the three locations with the most ratings. (Hint: They are U.S.A., France, and Canada, but find them out using codes.)  
```{r}
summary(choco$Company.Location)
```
Looking at the summary statistics, we can see that the US, France, and Canada have the greatest count of ratings.  

4.Create own question and answer:  

#How many different companies located in France?


```{r}
OnlyFrance <- choco[(choco$Company.Location=="France"), ]
summary(OnlyFrance$Company)
UniqueCompany <- unique(OnlyFrance$Company)
summary(UniqueCompany)
length(UniqueCompany)
```
  

Workflow: Overall, the workflow was smooth. We really had no issues that required a merge and to decide between two versions of a solution. In the future, however, I am sure it will require that.